### 2015-06-14 writing/S'15 LSTM/abstract.tex
Paper push.

\begin{abstract}
Tree-structured neural networks aim to deliver a robust and principled method for representing sentence meaning, but these models largely have not outperformed simpler sequence-based models by substantial margins. We hypothesize that sequence models like LSTMs are able to discover and implicitly use the same kinds of recursive compositional structures that the tree-structured ones are built around---at least in cases where there are clear cues to that structure in the data---mitigating the advantage of the tree-structured models. We investigate this possibility by evaluating both models on an artificial task for which recursive compositional structure is crucial, and find that the sequence model is able to exploit the underlying structure, though it is less efficient at learning than the tree models, only succeeding after exposure to a larger and richer set of training data.
\end{abstract}

>>>>

\begin{abstract}
Tree-structured neural networks aim to deliver a robust and principled method for representing sentence meaning, but these models largely have not outperformed simpler sequence-based models by substantial margins. We hypothesize that sequence models like LSTMs are able to discover and implicitly use the same kinds of recursive compositional structures that the tree-structured ones are built around---at least in cases where there are clear cues to that structure in the data---mitigating the advantage of the tree-structured models. We investigate this possibility by evaluating both models on an artificial task for which recursive compositional structure is crucial, and find that the sequence model is able to exploit the underlying structure, though it is less efficient at learning than the tree models, only succeeding after exposure to a larger and richer training set.
\end{abstract}

### 2015-06-14 writing/S'15 LSTM/methods.tex
Paper push.

\paragraph{Training} We randomly initialize all embeddings and layer parameters, and then train all parameters using minibatch stochastic gradient descent with AdaDelta \cite{zeiler2012adadelta} learning rates. Our objective is the standard negative log likelihood classification objective with L2 regularization. All models were stopped at 100 epochs (TODO), at which point all had largely converged without significantly declining from their peak performances.

>>>>

\paragraph{Training} We randomly initialize all embeddings and layer parameters, and then train all parameters using minibatch stochastic gradient descent with AdaDelta \cite{zeiler2012adadelta} learning rates. Our objective is the standard negative log likelihood classification objective with L2 regularization. All models were stopped after TODO gradient steps, at which point all had largely converged without significantly declining from their peak performances.
